Global code motion of congruent instructions

### 2017-09-16 cgo/paper.tex
adding for cgo

%% For double-blind review submission
\documentclass[acmlarge,review,anonymous]{acmart}\settopmatter{printfolios=true}
%\documentclass[acmlarge,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format should change 'acmlarge' to
%% 'sigplan,10pt'.

@@

\makeatletter\if@ACM@journal\makeatother

\makeatletter\preto{\@verbatim}{\topsep=1pt \partopsep=0pt}\makeatother

%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
\setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

@@

%% Title information
\title[SSA GCM]{Global code motion of congruent instructions}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \SPEC {SPEC Cpu 2006}
\def \gcm {global-code-motion}
\def \GCM {GCM}
\def \xlinux {x86\_64-linux}
\def \ooo {out-of-order}
%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.

\author{Aditya Kumar}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Senior Compiler Engineer}
  %\department{Department1}              %% \department is recommended
  \institution{Samsung Austin R\&D Center}            %% \institution is required
  %\streetaddress{Street1 Address1}
  \city{Austin}
  \state{Texas}
  %\postcode{Post-Code1}
  \country{USA}
}
\email{aditya.k7@samsung.com}

@@

%% Paper note
%% The \thanks command may be used to create a "paper note" ---
%% similar to a title note or an author note, but not explicitly
%% associated with a particular element.  It will appear immediately
%% above the permission/copyright statement.
\thanks{with paper note}                %% \thanks is optional
                                        %% can be repeated if necesary
                                        %% contents suppressed with 'anonymous'

@@

\ccsdesc[500]{Software and its engineering~Compilers}
\ccsdesc[500]{Software and its engineering~Source code generation}
\ccsdesc[500]{General and reference~Performance}

%\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{Optimizing Compilers, \GCC{}, \LLVM{}, Code Generation, Global Scheduling}  %% \keywords is optional

@@

\section{Introduction}
\label{sec:intro}
Compiler techniques to remove redundant computations are composed of an analysis
phase that detects identical computations in the program and a transformation
phase that reduces the number of run-time computations.  Classical scalar
optimizations like Common Subexpression Elimination (CSE) \cite{dragonbook} work
very well on single basic-blocks (local level) but when it comes to detect
redundancies across basic-blocks (global level) these techniques fall short:
more complex passes like Global Common Subexpression Elimination (GCSE) and
Partial Redundancy Elimination (\PRE{}) have been designed to handle these cases
based on data-flow analysis \cite{morel1979global}.  At first these techniques
were described in the classical data-flow analysis framework, but later the use
of Static Single Assignment (\SSA{}) representation lowered their cost in terms
of compilation time \cite{briggs1994effective,chow1997new,kennedy1999partial}
and brought these techniques in the main stream: nowadays \SSA{} based \PRE{} is
available in industrial compilers like \GCC{} and \LLVM{}.

@@

In this program the computations of tmax and tmin are identical to the
computations of tmin and tmax of sibling branch respectively. Both tmax and tmin
depend on inv which depends on a division operation which is generally more
expensive than the addition, subtraction, and multiplication operations. The
total latency of computation across each branch is: $C_{div} + 2(C_{sub} + C_{mul})$.
For an \ooo{} processor with two add units and two multiply
units, the total latency of computation is $C_{div} + C_{sub} + C_{mul}$.

Now if the computation of tmax and tmin are hoisted outside the
conditionals, the C code version would look like this:
\begin{verbatim}
float fun(float d, float min, float max, float a) {
  float inv = 1.0f / d;
  float x = (min - a) * inv;
  float y = (max - a) * inv;
  float tmin = x, tmax = y;
  if (inv < 0) { tmin = y; tmax = x; }
  return tmax + tmin;
}
\end{verbatim}

@@

\newpage

%% Bibliography
\bibliography{Bibliography}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,10pt,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall,10pt]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%% Title information
\title[SSA GCM]{Global code motion of congruent instructions}         %% [Short Title] is optional;

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \SPEC {SPEC Cpu 2006}
\def \gcm {global-code-motion}
\def \GCM {GCM}
\def \xlinux {x86\_64-linux}
\def \ooo {out-of-order}

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{Aditya Kumar}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Senior Compiler Engineer}
  %\department{Department1}              %% \department is recommended
  \institution{Samsung Austin R\&D Center}            %% \institution is required
  %\streetaddress{Street1 Address1}
  \city{Austin}
  \state{Texas}
  %\postcode{Post-Code1}
  \country{USA}
}
\email{aditya.k7@samsung.com}

@@

@@

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

@@

\section{Introduction}

\label{sec:intro}
Compiler techniques to remove redundant computations are composed of an analysis
phase that detects identical computations in the program and a transformation
phase that reduces the number of run-time computations.  Classical scalar
optimizations like Common Subexpression Elimination (CSE) \cite{dragonbook} work
very well on single basic-blocks (local level) but when it comes to detect
redundancies across basic-blocks (global level) these techniques fall short:
more complex passes like Global Common Subexpression Elimination (GCSE) and
Partial Redundancy Elimination (\PRE{}) have been designed to handle these cases
based on data-flow analysis \cite{morel1979global}.  At first these techniques
were described in the classical data-flow analysis framework, but later the use
of Static Single Assignment (\SSA{}) representation lowered their cost in terms
of compilation time \cite{briggs1994effective,chow1997new,kennedy1999partial}
and brought these techniques in the main stream: nowadays \SSA{} based \PRE{} is
available in industrial compilers like \GCC{} and \LLVM{}.

@@

In this program the computations of $tmax$ and $tmin$ are identical to the
computations of $tmin$ and $tmax$ of sibling branch respectively. Both $tmax$ and $tmin$
depend on $inv$ which depends on a division operation which is generally more
expensive than the addition, subtraction, and multiplication operations. The
total latency of computation across each branch is: $C_{div} + 2(C_{sub} + C_{mul})$.
For an \ooo{} processor with two add units and two multiply
units, the total latency of computation is $C_{div} + C_{sub} + C_{mul}$.

Now if the computation of $tmax$ and $tmin$ are hoisted outside the
conditionals, the C code version would look like this:
\begin{verbatim}
float fun(float d, float min, float max, float a) {
  float inv = 1.0f / d;
  float x = (min - a) * inv;
  float y = (max - a) * inv;
  float tmin = x, tmax = y;
  if (inv < 0) { tmin = y; tmax = x; }
  return tmax + tmin;
}
\end{verbatim}

@@

%% Bibliography
\bibliography{Bibliography}
%\bibliography{bibfile}
